---
title: "CIS 205 Course Assessment Summary"
output:
  html_document:
    df_print: paged
  fig_width: 4
  fig_height: 4
  html_notebook: default
  pdf_document: default
  word_document: default
---
<style>
        table {
            width: 350px;
            border-collapse: collapse;
        }
@media print {
      .pagebreak { page-break-before: always; }
    }
    </style>
<font size="4">
Instructors: **Craig Nelson**  
Course Sections: **001, 950, 951**  
Semester: **Fall 2020**  
Performance Goal: **75% of students meet or exceed expectations.**  
  
<center>
<table>
    <tr>
        <th colspan="2"><u>Performance Rubric</u></th>
    </tr>
    <tr>
        <td>Below Expectations (1):</td>
        <td>0 - 69.9%</td>
    </tr>
    <tr>
        <td>Meets Expectations (2):</td>
        <td>70% - 89.9%</td>
    </tr>
    <tr>
        <td>Exceeds Expectations (3):</td>
        <td>90% - 100%</td>
    </tr>
</table>
</font>
</center>
****
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center",  warning=FALSE, message=FALSE}
source("CourseProcessor.R")
fig.dim = c(6, 6)
course_processor("CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
<font size="3">
**Course Learning Outcome 1**: Use a modern database management program such as Oracle, MySQL and PostgreSQL to perform such tasks as writing operational and correct SQL (DDL, DML and DCL) statements.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center",  warning=FALSE, message=FALSE}
source("CLOProcessor.R")
fig.dim = c(6, 6)
processor(1, "CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 2**: Write SQL statements that perform fundamental database concepts, including Relational Algebra, and successfully use a Relational Database System.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center"}
processor(2, "CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 3**: Create and translate Entity Relationship (ER) Diagrams using a software diagramming tool.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center"}
processor(3, "CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 4**: Explain common ethical issues related to the use of information technology systems and the handling of data, including privacy and security issues.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center"}
processor(4, "CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 5**: Write operational and correct SQL (DDL, DML and DCL) statements.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center"}
processor(5, "CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 6**: Describe new concepts and terminology in DBMS such as Data Warehousing, Data Mining, NoSQL and Big Data.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center"}
processor(6, "CIS205.csv", "CIS205")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 7**: Implement a relational database from initial requirements and conceptual design (ER Diagram) to the physical database in a modern enterprise relational database management system.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center"}
processor(7, "CIS205.csv", "CIS205")
```
</center>
</font>