---
title: "CSCI 213 Course Assessment Summary"
output:
  html_document:
    df_print: paged
  fig_width: 4
  fig_height: 4
  html_notebook: default
  pdf_document: default
  word_document: default
---
<style>
        table {
            width: 350px;
            border-collapse: collapse;
        }
@media print {
      .pagebreak { page-break-before: always; }
    }
    </style>
<font size="4">
Instructors: **Craig Nelson**  
Course Sections: **950**  
Semester: **Fall 2020**  
Performance Goal: **75% of students meet or exceed expectations.**  
  
<center>
<table>
    <tr>
        <th colspan="2"><u>Performance Rubric</u></th>
    </tr>
    <tr>
        <td>Below Expectations:</td>
        <td>0 - 69.9%</td>
    </tr>
    <tr>
        <td>Meets Expectations:</td>
        <td>70% - 89.9%</td>
    </tr>
    <tr>
        <td>Exceeds Expectations:</td>
        <td>90% - 100%</td>
    </tr>
</table>
</font>
</center>
****
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center",  warning=FALSE, message=FALSE}
source("CourseProcessor.R")
fig.dim = c(6, 6)
course_processor("CSCI213.csv", "CSCI213")
```
</center>
<div class="pagebreak"> </div>
****
<font size="3">
**Course Learning Outcome 1**: Diagram the digital components of computing architecture and evaluate them for accuracy.  
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center",  warning=FALSE, message=FALSE}
source("CLOProcessor.R")
fig.dim = c(6, 6)
processor(1, "CSCI213.csv", "CSCI213")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 2**: Choose the optimal format to represent numerical and non-numerical data by estimating their memory requirements and how this choice could affect accuracy and precision.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center"}
processor(2, "CSCI213.csv", "CSCI213")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 3**: Describe complex and reduced instruction set computing and apply the concepts of an instruction set architecture through the use of an assembly language.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center"}
processor(3, "CSCI213.csv", "CSCI213")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 4**: Identify interrupt mechanisms and describe ways I/O control, data transfer, and dataflow are implemented.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center"}
processor(4, "CSCI213.csv", "CSCI213")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 5**: Explain the design and implementations of different types of storage devices, memory hierarchy, cache memory, and addressing schemes.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center"}
processor(5, "CSCI213.csv", "CSCI213")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 6**: Describe the functional components of a modern central processing unit and how processor performance can be improved by pipelining and superscalar architectures.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center"}
processor(6, "CSCI213.csv", "CSCI213")
```
</center>
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 7**: Examine the essential concepts of parallel processing, multicore and multithreaded processors, GPUs and special-purpose processors.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=6, fig.align="center"}
processor(7, "CSCI213.csv", "CSCI213")
```
</center>
</font>
