---
title: "CSCI 112 Course Assessment Summary"
output:
  html_document:
    df_print: paged
  fig_width: 4
  fig_height: 4
  html_notebook: default
  pdf_document: default
  word_document: default
---
<style>
        table {
            width: 350px;
            border-collapse: collapse;
        }
@media print {
      .pagebreak { page-break-before: always; }
    }
    </style>
<font size="4">
Instructors: **Charles Herbert, Craig Nelson**  
Course Sections: **001, 900**  
Semester: **Fall 2020**  
Performance Goal: **75% of students meet or exceed expectations.**  
  
<center>
<table>
    <tr>
        <th colspan="2"><u>Performance Rubric</u></th>
    </tr>
    <tr>
        <td>Below Expectations:</td>
        <td>0 - 69.9%</td>
    </tr>
    <tr>
        <td>Meets Expectations:</td>
        <td>70% - 89.9%</td>
    </tr>
    <tr>
        <td>Exceeds Expectations:</td>
        <td>90% - 100%</td>
    </tr>
</table>
</font>
</center>
****
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center",  warning=FALSE, message=FALSE}
source("CourseProcessor.R")
fig.dim = c(6, 6)
course_processor("CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
<font size="3">
**Course Learning Outcome 1**: Create object-oriented software that implements aggregation, inheritance, and polymorphism independently and as a member of a team.  
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center",  warning=FALSE, message=FALSE}
source("CLOProcessor.R")
fig.dim = c(6, 6)
processor(1, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 2**: Create event-driven software that implements event handling to respond to user-generated events and program exceptions.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(2, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 3**: Evaluate software based on specification documents and validate software through test plans, integration tests, and unit tests independently and as a member of a team.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(3, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 4**: Describe the use and importance of Application Programming Interfaces (APIs) in modern software development and create software that uses APIs.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(4, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 5**: Implement elementary iterative searching and sorting algorithms and discuss algorithm complexity and factors that influence the choice of an algorithm..
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(5, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 6**: Describe the concept of recursion and develop software using recursive solutions to common problems in computing.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(6, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 7**: Use electronic spreadsheets to organize, analyze, and present data related to the temporal and spatial complexity of algorithms.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(7, "CSCI112.csv", "CSCI112")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 8**: Use a database management system and create software that securely interacts with a database.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(8, "CSCI112.csv", "CSCI112")
```
</center>
</font>