---
title: "CSCI 111 Course Assessment Summary"
output:
  html_document:
    df_print: paged
  fig_width: 4
  fig_height: 4
  html_notebook: default
  pdf_document: default
  word_document: default
---
<style>
        table {
            width: 350px;
            border-collapse: collapse;
        }
@media print {
      .pagebreak { page-break-before: always; }
    }
    </style>
<font size="4">
Instructors: **Michael Hackett, Charles Herbert**  
Course Sections: **001, 002, 900, 901**  
Semester: **Fall 2020**  
Performance Goal: **75% of students meet or exceed expectations.**  
  
<center>
<table>
    <tr>
        <th colspan="2"><u>Performance Rubric</u></th>
    </tr>
    <tr>
        <td>Below Expectations:</td>
        <td>0 - 69.9%</td>
    </tr>
    <tr>
        <td>Meets Expectations:</td>
        <td>70% - 89.9%</td>
    </tr>
    <tr>
        <td>Exceeds Expectations:</td>
        <td>90% - 100%</td>
    </tr>
</table>
</font>
</center>
****
<center>
```{r, echo=FALSE, results='hide', fig.width=6.5, fig.height=6, fig.align="center",  warning=FALSE, message=FALSE}
source("CourseProcessor.R")
fig.dim = c(6, 6)
course_processor("CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
<font size="3">
**Course Learning Outcome 1**: Describe the general history of programming languages, programming paradigms, the use of virtual machines, and effects of scale on programming methodology.  
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center",  warning=FALSE, message=FALSE}
source("CLOProcessor.R")
fig.dim = c(6, 6)
processor(1, "CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 2**: Create, implement, test, and debug computer programs that use basic computation, simple I/O, standard conditional and iterative structures, and subroutines while working in a group or independently.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center",  warning=FALSE, message=FALSE}
processor(2, "CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 3**: Describe the essential properties of algorithms and develop algorithms for the solution of specific problems in computing.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(3, "CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 4**: Identify and describe declaration models, type-checking, and the properties of variables and sequence types.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(4, "CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 5**: Describe the fundamental concepts and philosophies of object-oriented programming, and design and create object-oriented software independently and working in a group.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(5, "CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 6**: Use word processing and presentation software to produce academic and professional documents, individually and working in collaboration with others in a learning management system.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(6, "CSCI111.csv", "CSCI111")
```
</center>
<div class="pagebreak"> </div>
****
**Course Learning Outcome 7**: Explain common ethical issues related to the use of information technology systems and the handling of data, including privacy and security issues.
  
<center>
```{r, echo=FALSE, results='hide', fig.width=8, fig.height=8, fig.align="center"}
processor(7, "CSCI111.csv", "CSCI111")
```
</center>
</font>